Counterfactuals from SVARs - Questions

### 2018-01-09 Latex/Meeting_Ryan_10Jan_2018/meeting10Jan2018.tex
some work on counterfactual

\title{Discussion of Results}
\author{Marco Brianti\\Laura Gati}
\date{22 Nov 2017}

@@

\subsection*{Shares of FEV of TFP}

@@

\textbf{Differenced relative prices (inflation of IT price index over CPI-inflation)}

IT: 51.60\%

\noindent News: 19.63\%

@@

 \textbf{Log level of capital prices (differencing here seems to overdo it)}

IT: 28.47\%

\noindent News: 28.31\%

\newpage
\subsection*{IRFs - ratio of inflations (i.e relative prices)}

\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{\ourFigPath Figures/fig_News_shock_Ryan_two_stepsID_20-Nov-2017_12_24_34}
\caption{News shock - ratio of inflations}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{\ourFigPath Figures/fig_IT_shock_Ryan_two_stepsID_20-Nov-2017_12_24_39}
\caption{IT shock - ratio of inflations}
\end{figure}

%%%%%
\newpage
\subsection*{IRFs - log level of capital prices}

\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_21-Nov-2017_11_35_24}
\caption{News shock - log level of capital prices}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_21-Nov-2017_11_35_27}
\caption{IT shock - log level of capital prices}
\end{figure}

\newpage
\subsection*{Recap and interpretation}

\begin{itemize}
\item One big motivation for the entire research project is the puzzling decrease in TFP growth, which - as we have also documented - started \emph{before} the Great Recession.
\item The sudden decrease in IT investment after the burst of the IT bubble around 2000-2002 coincides with this slowdown in TFP growth, which led us to investigate the effect of IT investment on TFP. 
\item We run a structural VAR to estimate the effect of an IT productivity shock on TFP and other main macroeconomic variables.
\item This identification poses a challenge because we need to confront the view that there is an endogenous channel in the evolution of TFP with the widely accepted view that TFP is driven by news. Since both are similar in the way they affect TFP only with lags, we need an additional restriction to disentangle the two.
\item The additional restriction we use is that news shocks should have no effect on relative IT prices at a certain (long) horizon, because they behave like demand shocks.
\item [] \textbf{What the results seem to suggest:}
\item [1)] News and IT shocks together explain more of the FEV of TFP than news does alone in Barsky \& Sims (around 70\% vs approximately 40\% in Barsky \& Sims). (Compare with capital prices specification too.)
\item [2)] News still explains a considerable fraction, but IT shocks explain more. (Compare with capital prices specification too.)
\item [] $\rightarrow$ we read this as evidence that both news and the endogenous channel via IT investment plays an important role in explaining TFP  over the business cycle and the medium run. 
\end{itemize}

\subsection*{Comments? Thoughts? Does this make sense to you? Is it presentable in its current form?}

>>>>

\title{Counterfactuals from SVARs - Questions}
\author{Marco Brianti\\Laura Gati}
\date{10 Jan 2018}

@@

@@

\section{What we have done so far:}
\begin{enumerate}
\item Recovered structural shocks from our identified VAR
\item Used them together with the impulse responses to generate what Kilian calls ``cumulative contribution of a shock $j$" to TFP. These are historical decompositions of TFP in the sense that, relative to the trend of our TFP series, we can see the percent deviations caused by the shocks - together with the responses to them - in our sample. Mathematically, the cumulative effect of a shock $j$ on TFP is:

\begin{equation}
\hat{y}^{j}_{TFP, t} = \sum^{t-1}_{i=0} B(L)^i A s_{j, t-i}
\end{equation}

where $j = \{IT, news\}$ and $s$ is the structural shock. Then, the overall cumulative effect of all shocks is

\begin{equation}
\hat{y}_{TFP, t} = \sum_{j= IT,news} \hat{y}^{j}_{TFP, t}
\end{equation}

\item The object we're interested in is
\begin{equation}
TFP - f\big( \hat{y}^{IT}_{TFP, t} \big)
\end{equation}

and our question is: what is $f$?

@@

In other words: the problem comes from the fact that $\hat{y}^{IT}_{TFP, t}$ is in percentage deviations from the trend of TFP. What we're interested in, however, is how TFP would have evolved (in levels) absent the shocks to IT starting in 2000-Q3.

\end{enumerate}
